A Streaming Algorithm for 2-Center with Outliers in High Dimensions

### 2015-04-29 paper.tex
Revise query section and corresponding algorithm

\newcommand{\set}[1]{\left\{ #1 \right\}}
\newcommand{\seq}[1]{\left< #1 \right>}
\newcommand{\ceil}[1]{\left\lceil{#1}\right\rceil}
\newcommand{\floor}[1]{\left\lfloor{#1}\right\rfloor}
\newcommand{\card}[1]{\left|{#1}\right|}
\newcommand{\len}[1]{\|{#1}\|}
\newcommand{\setcomp}[1]{\overline{#1}}
\newcommand{\provided}{\,|\,}

@@

\begin{obs}
\label{obs:intersection}
	Let $B_1$ and $B_2$ be two disjoint balls of distance greater than $\delta$,
	and let $B$ be an arbitrary ball of radius at most $\frac{\delta}{2}$. 
	Then $B$ intersects at most one of $B_1$ and $B_2$.
\end{obs}

@@

\begin{lemma}
\label{lem:}
	If $p \in B_1^*$ and $q \in B_2^*$,
	then at most $z$ points of $P$ lie outside $B(p, 2r^*) \cup B(q, 2r^*)$.
\end{lemma}

\begin{proof}
	TBA.
\end{proof}

\begin{lemma}
\label{lem:}
	Let $S$ be a subset of $P$ of size at least $\dz$,
	enclosed by a ball of radius $\delta^* / 2$.
	Then the centerpoint of $S$ lies either inside $B_1^{*}$ or inside $B_2^{*}$.
\end{lemma}

\begin{proof}
	TBA.
\end{proof}

\paragraph{The Algorithm}
We now describe our algorithm for handling the case  $\delta^* > \alpha r^*$.
At any time, our algorithm maintains a partition of $P$ into three disjoint subsets
$B_1$, $B_2$, and Buffer.
The first point $p_1$ is assumed, w.l.o.g, to be in $B_1^*$. 
The algorithm tries to partition points in such a way that 
at the end,
$B_1$ contains the whole $B_1^*$, and $B_2$ contains the whole $B_2^*$,
with possibly some outliers being contained in $B_1$ and $B_2$.
%Buffer has always size at most $z$.
The algorithm sets $c_1 = p_1$ as the fixed center of $B_1$,
and picks $c_2$ among the points processed so far as a candidate center for $B_2$.
Moreover, the algorithm maintains two values $\delta$ and $r$,
where at any time, $\delta$ is a lower bound of $\delta^*$, 
and $r$ is an upper bound of $2r^*$.

@@

\begin{algorithm}[t]
\caption{\sc 2-CenterCase1$(P)$} 
\algsetup{indent=1.5em}
\label{alg:case-1}
\begin{algorithmic}[1]
\STATE $c_1 \gets p_1$, $\rc  \gets 0$, $\delta \gets 0$
\FORALL{$p \in P$}
	\IF {\NOT (\Call{AddToB$_1$}{$p$} \OR \Call{AddToB$_2$}{$p$})}
		\STATE add $p$ to Buffer
		\WHILE{$\card{\mbox{Buffer}} > z$} \label{step:buffer-overflow}
			\IF{$\card{B_2} \ge \dz$}
				\STATE $B_1 \gets B_1 \cup B_2$, $B_2 \gets \emptyset$
			\ELSIF{$c_2$ is set}
				\STATE $B_1 \gets B_1 \cup \set{c_2}$ %, $B_u \gets B_u \cup \set{c_2}$
				%\STATE remove $c_2$ from $B_2$
			\ENDIF
			\STATE $T \gets \mbox{Buffer} \cup B_2 \setminus \set{c_2}$
			\STATE $B_2 \gets \emptyset$ 
%			\IF{first iteration of while}
%				\FOR{$p \in T$}
%					\IF{\Call{AddToB$_1$}{$p$}}
%						\STATE remove $p$ from $T$
%					\ENDIF
%				\ENDFOR
%			\ENDIF
			\STATE $c_2 \gets$ an arbitrary point of $T$
			\STATE $\rc  \gets \frac{2}{\alpha}\len{c_1 c_2}$
			\FOR{$p \in T$}
				\STATE \Call{AddToB$_2$}{$p$}
			\ENDFOR				
			\STATE $\mbox{Buffer} \gets T \setminus B_2$
		\ENDWHILE
	\ENDIF
\ENDFOR
\end{algorithmic}
\end{algorithm}

@@

\begin{enumerate}
\item [(a)] $\delta < \delta^*$ %$\delta$ is a lower bound of $\delta^*$
\item [(b)] $B_1 \cap B_2^* = \emptyset$
\item [(c)]  if $\cp \in B_2^*$, then 
	\begin{enumerate}
		\item [1.] $2r^* \le r \le \delta /2$
		\item [2.] $B_2 \cap B_1^* = \emptyset$
		\item [3.] all points in $\Buffer$ are outliers
	\end{enumerate}
\end{enumerate}
\end{lemma}

\begin{proof}
TBA \ 
(All non-used parts from the previous version are copied here.
They might be useful for composing the proof of this lemma.)

The function \textproc{AddToB$_1$} presented in \Cref{alg:addB1} 
is used to add a point $p$ to $B_1$. 
%The point $c_1$ is the first point of the stream,
%which is assumed to be non-outlier, and is in $B_1^*$.
The point will be added to $B_1$ only if it is within distance $\delta$ of the center $c_1$, 
where $\delta = \frac{\alpha}{\alpha+4}\len{qc_1}$ 
and $q$ is the $(z+1)$-furthest point from $c_1$.
%among the points of $P$ seen so far.
By Lemma~\ref{lem:(z+1)-furthest}, $\delta$ is a strict lower bound of $\delta^*$. 
Therefore, any point within $\delta$-radius of $c_1$ is guaranteed to be outside $B_2^*$. 
Thus, property P1 is not violated by this function.
%$B_1 \cap B_2^* = \emptyset$.
Note that if less than $z+1$ points have been seen so far,
then $\delta = 0$, %$q = c_1$, 
and hence, property P1 is still maintained.

The function \textproc{AddToB$_2$} presented in \Cref{alg:addB2}
is used to add a point $p$ to $B_2$.
Initially, $B_2$ is empty and $c_2$ is not initialized. 
When an appropriate candidate is found, 
$c_2$ is set to that candidate by the main algorithm (Algorithm~\ref{alg:case-1}),
and $\rc$ is set to $\frac{2}{\alpha}\len{c_1c_2}$.
After that, points are added to $B_2$ by function \textproc{AddToB$_2$}
only if they are within $\rc$-radius of $c_2$. 
Consider $c_2$ as the central point $c_p$. % is considered as the central point $\cp$. 
Clearly, property P2 holds initially when $B_2$ consists of a single point $c_2$. 
All subsequent points added to $B_2$ are within $\rc$-radius of $c_2$.
Therefore, for $\alpha > 7$ (Why?), Observation~\ref{obs:intersection}
implies that $B_2 \cap B_1^* = \emptyset$,
and hence, property P2 is maintained. %invariant under this operation.

When the size of $B_2$ reaches $\dz$, 
we update the central point $\cp$ to the centerpoint of $B_2$.
%We claim that $B(c_2, (2 + \frac{2}{\alpha})\rc )$ completely covers
%the ball $B(\cp, \frac{2\len{c_1\cp}}{\alpha})$.
If $\cp \in B_2^*$, then by Observation~\ref{obs:c+4},
we have $\frac{\len{c_1\cp}}{\delta^*} \geq 1$,
and hence, $r^* < \frac{\len{c_1\cp}}{\alpha}$. 
Therefore, $B_2^* \subset B(\cp, \frac{2\len{c_1\cp}}{\alpha})$.
Moreover,
\[
	2 \cdot \frac{\len{c_1\cp}}{\alpha} \leq \frac{2}{\alpha}(\len{c_1c_2} + \rc ) 
	\leq (1 + \frac{2}{\alpha})\rc.
\]
Therefore, $B_2^* \subseteq B(c_p, (1 + \frac{2}{\alpha})\rc )
\subseteq B(c_2, (2 + \frac{2}{\alpha})\rc )$. 
It is easy to see that $(2 + \frac{2}{\alpha})\rc  \le \frac{\delta}{2}$ provided that $\alpha \ge 14$.
Thus, if we increase $\rc$ by a factor of $(2 + \frac{2}{\alpha})$, 
%by setting $B_2 = B(c_2, (2 + \frac{2}{\alpha})\rc )$, 
$B_2 \cap B_1^* = \emptyset$
by Observation~\ref{obs:intersection}, and hence,
property P2 is still maintained.

Whenever the buffer overflows 
%the assumption about $\cp \in B_2^*$ is contradicted.
%At some point during the execution of Algorithm~\ref{alg:case-1}, the assumption about $\cp \in B_2^*$ might be contradicted when the buffer overflows. We can then conclude that
% $\cp \notin B_2^*$.
the algorithm takes one of the following actions
depending on the size of $B_2$.

\begin{itemize}
\item 
If $|B_2| < \dz$, then $c_2$ can be added to $B_1$
without violating P1. (Why?) 
The algorithm then tries the points in $B_2 \cup \mbox{Buffer}$, 
until it finds a suitable candidate for $c_2$ that does not leave
more than $z$ points uncovered. 
Note that at most $(z+1)(d+1) + z$ points have to be tried.

\item 
If $\card{B_2} \ge \dz$, let $q$ be the $(z+1)$-furthest point from $p_1$,
and let $p'$ be the nearest point of the ball $B_2(c_2, \rc )$ to $p_1$. 
Then $\len{qp_1} > \len{p'p_1}$, since $B_2$ contains more than $z+1$ points. 
Therefore, by Lemma~\ref{lem:(z+1)-furthest} we have
\[
\delta \ge \frac{\alpha }{\alpha+4}\len{qp_1} \ge \frac{\alpha}{\alpha+4} (\len{c_1c_2} - \rc ) = \frac{\alpha^2 - 2\alpha}{2\alpha + 8} \rc.
\]
As a result, if $\alpha \geq 14$ then $(2 + \frac{2}{\alpha}) \rc  < \frac{\delta}{2}$. 
By Observation~\ref{obs:intersection}, the ball $B_2(c_2, (2 + \frac{2}{\alpha}) \rc )$ 
has nonempty intersection with exactly one of $B_1^*$ and $B_2^*$ 
(i.e., not all of its points can be outliers). 
Since the buffer overflowed, the assumption about the central point, 
$\cp$, being in $B_2^*$ has become invalid. 
By Observation~\ref{obs:omitting-centerpoint}, if $\cp$ is not covered, 
then the ball $B_1^*$ leaves at least $z+1$ points of $B_2$ uncovered, 
and there will be more than $z$ outliers. 
Thus, $\cp$ has to be covered. 
As a result, $\cp \in B_1^*$ and all the points of $B_2$ can be added to $B_1$. 
This is done by replacing $B_1$ with $B_1 \cup B_2$, and resetting $B_2$ to empty set.
\end{itemize}
\end{proof}

\begin{lemma}
\label{lem:}
	After termination of \Cref{alg:case-1}, 
	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
	then $B_2 \cap B_2^* = \emptyset$.
\end{lemma}

\begin{proof}
	TBA.
\end{proof}

@@

Let $B_1'$, $B_2'$, and $B_u'$ be the $\beta$-approximate balls obtained from the data structures
[This part needs clarification].
%1-centers obtained from $B_1$, $B_2$ and $B_u$ by the $\beta$-approximation algorithm, respectively. 
To answer a query, we can use these balls as follows. 
By our initial assumption about $p_1$, $B_1$ contains $B_1^*$,
and $B_1'$ is a $\beta$-approximation for $B_1^*$. (Why?)
But for $B_2$, it might be the case that our assumption about $c_2$ 
was incorrect, so $B_2'$ may not be a good approximation for $B_2^*$. 
There are two cases to be considered based oon $\card{B_2}$. 
If $\card{B_2} < (z+1)(d+1)$, then we can try each point in 
$B_2 \cup \mbox{Buffer}$ as a candidate for the central point. 
If $\card{B_2} \ge \dz$, then there is no need for points in $B_2$ to be considered, 
since for those points as central point, $B_1$ will be replaced by $B_u$ and $B_2$ will be empty. (Why?)
Thus it suffices to consider points of Buffer as candidates 
and compare them to the solution of $(B_u, \emptyset)$.

\begin{algorithm}
\caption{\sc Query} 
\algsetup{indent=1.5em}
\label{alg:query}
\begin{algorithmic}[1]
%\Function{Query}{}
	\STATE solutions $\gets [\Call{ComputeMin}{B_u, \emptyset, \text{Buffer}}]$

	\STATE candidates $\gets$ Buffer
	\IF {$\card{B_2} < \dz$}
		\STATE candidates $\gets \text{Buffer} \cup B_2$ % \setminus \set{c_2}$
	\ENDIF

	\FOR{$c_2 \in$ candidates}
		\STATE $\rc  \gets \frac{2}{\alpha} \len{c_1 c_2}$
		\STATE $B_2 \gets \emptyset$, Buffer $\gets \emptyset$ 
		\FOR{$p \in$ candidates}
			\IF{\NOT \Call{AddToB$_2$}{$p$}}
				\STATE add $p$ to Buffer
			\ENDIF
		\ENDFOR
		\STATE add \Call{ComputeMin}{$B_1$, $B_2$, Buffer} to solutions
	\ENDFOR
	\RETURN $\min\set{\text{solutions}}$
%\EndFunction
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{\sc ComputeMin($B_1, B_2, \text{\rm Buffer}$)} 
\algsetup{indent=1.5em}
\label{alg:query}
\begin{algorithmic}[1]
%\Function{ComputeMin}{$B_1$, $B_2$, Buffer}
	\STATE solutions $\gets [\,]$
	\FOR{$k \gets 0, \dots,(z - \card{\mbox{Buffer}})$}
		\STATE $r_1 \gets \Call{1-Center}{B_1, k}$
		\STATE $r_2 \gets \Call{1-Center}{B_2, z - \card{\mbox{Buffer}} - k}$
		\STATE add $\max \set{r_1, r_2}$ to solutions
	\ENDFOR
	\RETURN $\min\set{\text{solutions}}$
%\EndFunction
\end{algorithmic}
\end{algorithm}

@@

\subsection{The Case $\delta^* \leq \alpha r^*$}
\label{subsec:smaller}
Our idea in this section is derived from~\cite{ahn2014computing, kim2014improved}. To avoid duplication, we just outline the important parts of their algorithm and our modifications to it. Kim's algorithm has $10$ different states. In each step one or many of the states can be valid and their algorithm considers all of them in parallel. In each state, there exist at most two balls. A transition between the states occurs whenever a point not covered by any of the two balls has arrived in the stream. This transition graph starts with a blank node (with no balls) and has depth four (without considering the end nodes). It is straightforward to see that this transition graph is a DAG.
Our modification is on the transition part.
Points that are covered by current solution can safely be ignored, as they do not cause any transitions in the state, and only those points that lie outside the solution are candidates for being an outlier.
In each state the number of points that should be considered as outliers is unknown. So all the possible choices should be considered. It is sufficient to have four integers, $n_1,\dots, n_4$ representing the number of outliers in depth $1$ to $4$, such that $\sum_{i=1}^{4} n_i=z$. 
The modified algorithm is presented in \Cref{alg:smallc}.
In this algorithm, \textproc{NthOutlier}$(n,p)$ returns the $n$-th point 
arriving after $p$ in $P$ that does not lie in the current candidate solution.

>>>>

\newcommand{\set}[1]{\left\{ #1 \right\}}
\newcommand{\seq}[1]{\left< #1 \right>}
\newcommand{\ceil}[1]{\left\lceil{#1}\right\rceil}
\newcommand{\floor}[1]{\left\lfloor{#1}\right\rfloor}
\newcommand{\card}[1]{\left|{#1}\right|}
\newcommand{\len}[1]{\|{#1}\|}
\newcommand{\radius}[1]{\frac{2}{\alpha} \len{c_1 #1}}
\newcommand{\setcomp}[1]{\overline{#1}}
\newcommand{\provided}{\,|\,}

@@

\begin{obs}
\label{obs:intersection}
	Let $B_1$ and $B_2$ be two disjoint balls of distance equal to $\delta$,
	and let $B$ be an arbitrary ball of radius less than $\frac{\delta}{2}$. 
	Then $B$ intersects at most one of $B_1$ and $B_2$.
\end{obs}

@@

\begin{lemma}
\label{lem:2r}
	If $p \in B_1^*(c_1, r^*)$ and $q \in B_2^*(c_2, r^*)$,
	then $B_1^* \subset B(p, 2r^*)$ and $B_2^* \subset B(q, 2r^*)$ and as a result at most $z$ points of $P$ lie outside $B(p, 2r^*) \cup B(q, 2r^*)$.
\end{lemma}

\begin{proof}
	For an arbitrary point $p' \in B_1^*$, $\len{pp'} \leq \len{pc_1} + \len{p'c_1} \leq 2r^*$ and as a result $B_1^* \subset B(p, 2r^*)$(With similar proof, $B_2^* \subset B(q, 2r^*)$).  Considering that at most $z$ points of $P$ is outlier,  the proof is complete.
\end{proof}

\begin{lemma}
\label{lem:center-point}
	Let $S$ be a subset of $P$ of size at least $\dz$,
	enclosed by a ball $B$ of radius less than $\delta^* / 2$.
	Then the centerpoint $c_p$ of $S$ lies either inside $B_1^{*}$ or inside $B_2^{*}$.
\end{lemma}

\begin{proof}
	By Observation~\ref{obs:intersection}, ball $B$ intersects exactly one of $B_1^*$ and $B_2^*$ (all points of $S$ can not be outlier). Without loss of generality, Let $B$ intersect with $B_1^*$. By Observation \ref{obs:omitting-centerpoint}, $c_p$ would lie in $B_1^*$ and the proof is complete.
\end{proof}

\paragraph{The Algorithm}
We now describe our algorithm for handling the case  $\delta^* > \alpha r^*$.
At any time, our algorithm maintains a partition of $P$ into three disjoint subsets
$B_1$, $B_2$, and Buffer.
The first point $p_1$ is assumed, w.l.o.g, to be in $B_1^*$. 
The algorithm tries to partition points in such a way that 
at the end,
$B_1$ contains the whole $B_1^*$, and $B_2$ contains the whole $B_2^*$,
with possibly some outliers being contained in $B_1$ and $B_2$.
%Buffer has always size at most $z$.
The algorithm sets $c_1 = p_1$ as the fixed center of $B_1$,
and picks $c_2$ among the points processed so far as a candidate center for $B_2$.
Moreover, the algorithm maintains two values $\delta$ and $r$,
where at any time, $\delta$ is a lower bound of $\delta^*$, 
and $r$ is an upper bound of $2r^*$ (if $c_p \in B_2^*$).

@@

\begin{algorithm}[t]
\caption{\sc 2-CenterCase1$(P)$} 
\algsetup{indent=1.5em}
\label{alg:case-1}
\begin{algorithmic}[1]
\STATE $c_1 \gets p_1$, $\rc  \gets 0$, $\delta \gets 0$
\FORALL{$p \in P$}
	\IF {\NOT (\Call{AddToB$_1$}{$p$} \OR \Call{AddToB$_2$}{$p$})}
		\STATE add $p$ to Buffer
		\WHILE{$\card{\mbox{Buffer}} > z$} \label{step:buffer-overflow}
			\IF{$\card{B_2} \ge \dz$}
				\STATE $B_1 \gets B_1 \cup B_2$, $B_2 \gets \emptyset$
			\ELSIF{$c_2$ is set}
				\STATE $B_1 \gets B_1 \cup \set{c_2}$ %, $B_u \gets B_u \cup \set{c_2}$
				%\STATE remove $c_2$ from $B_2$
			\ENDIF
			\STATE $T \gets \mbox{Buffer} \cup B_2 \setminus \set{c_2}$
			\STATE $B_2 \gets \emptyset$ 
%			\IF{first iteration of while}
%				\FOR{$p \in T$}
%					\IF{\Call{AddToB$_1$}{$p$}}
%						\STATE remove $p$ from $T$
%					\ENDIF
%				\ENDFOR
%			\ENDIF
			\STATE $c_2 \gets$ (z+1)-furthest point of $T$ from $c_1$
			\STATE $\rc  \gets \radius{c_2}$
			\FOR{$p \in T$}
				\STATE \Call{AddToB$_2$}{$p$}
			\ENDFOR				
			\STATE $\mbox{Buffer} \gets T \setminus B_2$
		\ENDWHILE
	\ENDIF
\ENDFOR
\end{algorithmic}
\end{algorithm}

@@

\begin{enumerate}
\item [(a)] $\delta < \delta^*$ %$\delta$ is a lower bound of $\delta^*$
\item [(b)] if $c_2$ is set, then
\begin{enumerate}
	\item[1.] $r \leq \delta/2$
	\item[2.] $B(c_p, \radius{c_p}) \subset B_2(c_2, r)$
\end{enumerate}
\item [(c)] $B_1 \cap B_2^* = \emptyset$
\item [(d)]  if $\cp \in B_2^*$, then 
	\begin{enumerate}
		\item [1.] $2r^* \le r$
		\item [2.] $B_2 \cap B_1^* = \emptyset$
		\item [3.] all points in $\Buffer$ are outliers
	\end{enumerate}

\end{enumerate}
\end{lemma}

\begin{proof} The proof consists of four parts and each part use previous parts:

Invariant (a): 
When a point $p$ arrives in the stream, \textproc{AddToB$_1$} is called, which tries to add $p$ to ball $B_1$.
By Lemma \ref{lem:(z+1)-furthest}, if point $q$ be the $(z+1)$-furthest point of the stream from $c_1$,
then $\frac{\alpha}{\alpha+4} \len{c_1q}$ is an increasing stream of lowerbounds for $\delta^*$. So at any point, $\delta < \delta^*$.

Invariant (b): 
When an appropriate candidate for $c_2$ is found, 
$c_2$ is set to that candidate by the main algorithm (Algorithm~\ref{alg:case-1}),
and $\rc$ is set to $\frac{2}{\alpha}\len{c_1c_2}$.
After that, points are added to $B_2$ by function \textproc{AddToB$_2$}
only if they are within $\rc$-radius of $c_2$.

If $c_2$ is set, then it is $(z+1)$-furthest points of a set $T \subset P$ from $c_1$. 
Let q be the $(z+1)$-furthest point of the Stream from $c_1$ at that state, then $\len{c_1c_2} \leq \len{c_1q}$ and since (for $16 \leq \alpha$) $\radius{c_2} \leq \frac{1}{6}\frac{\alpha \len{c_1 q}}{(\alpha + 4)} \leq \delta / 6$, then $$r \leq (2 + \frac{2}{\alpha})\radius{c_2} \leq 3 \radius{c_2}  \leq \delta /2$$.

In part 2, if $|B_2| < \dz$ then $c_p = c_2$ and $r = \radius{c_2}$, so $B_2 = B(c_p, \radius{c_p})$. 
When the size of $B_2$ reaches $\dz$, the central point $\cp$ moves to the centerpoint of $B_2$ and $\rc$ increases by a factor of $(2 + \frac{2}{\alpha})$. 
Because the centerpoint of $B_2$ locate in $B_2$, then $c_p \in B(c_2, \radius{c_2})$.
So if $|B_2| \ge \dz$ then $\len{c_2 c_p} \leq \radius{c_2}$ and as a result
$$\radius{c_p} \leq \frac{2 (\len{c_1 c_2} + \len{c_2 c_p})}{\alpha} \leq \radius{c_2}(1 + \frac{2}{\alpha})$$ 
So $B(c_p, \radius{c_p}) \subset B_2(c_2, \radius{c_2}(2 + \frac{2}{\alpha}))$.

Invariant (c): A point $p$ can be added to $B_1$ in two parts of the \Cref{alg:case-1}. 
First case is in function \textproc{AddToB$_1$}, the point will be added to $B_1$ only if it is within distance $\delta$ of the center $c_1$,  when $\len{pc_1} \leq \delta$, which due to invariant (a), guaranties $\len{pc_1} < \delta^*$, so $p \not \in B_2^*$.

Second case is in \Cref{alg:case-1}, whenever the buffer overflows and $B_2$ is non-empty the algorithm takes one of the following actions depending on the size of $B_2$.
If $|B_2| < \dz $, then $c_2 = c_p$. \Cref{alg:case-1} add $c_2$ to $B_1$.
By contradiction assume that $c_p \in B_2^*$, then due to invariant (b) part 1 and invariant (d) part 1, $2r^* \leq r \leq \delta/2 < \delta^*/2$. So by Lemma \ref{lem:2r}, there should be at most $z$ points outside $B_1 \cup B_2$ which contradicts overflow of the buffer.

If $|B_2| \geq \dz$, then $c_p$ is the centerpoint of the first $\dz$ points currently in $B_2$. 
In this case, we add all points of $B_2$ to $B_1$. Due to invariant (b), $r \leq \delta/2 < \delta^*/2$. 
So By Lemma \ref{lem:center-point}, $c_p \in B_1^*$ or $c_p \in B_2^*$. By contradiction assume that $c_p \in B_2^*$. In this case, due to invariant (d) part 1 and invariant (b) part 2, $B_2$ covers $B(c_p, \radius{c_p})$ and $2r^* \leq r$. similar to previous part, it contradicts overflow of the buffer.

Invariant (d): 
Due to  Observation \ref{obs:c+4}, if $c_1 \in B_1^*$ and $c_p \in B_2^*$ then $1 \leq \frac{\len{c_1 c_p}}{\delta^*} \leq \frac{\len{c_1 c_p}}{\alpha r^*}$ and as a result $2r^* \leq \radius{c_p}$. If $|B_2| < \dz$ then $c_p = c_2$ and By \Cref{alg:case-1}, $r = \radius{c_2}$, so $2r^* \leq r$.

If $|B_2| \ge \dz$ then similar to invariant (b): $$2r^* \leq \radius{c_p} \leq (1 + \frac{2}{\alpha})\radius{c_2} \leq (2 + \frac{2}{\alpha})\radius{c_2} = r$$

In part 2, due to previous part, if $c_p \in B_2^*$ then $2r^* \leq r \leq \delta /2$ and $c_p \in B_2$. Due to invariant (a) and Observation \ref{obs:intersection}, $B_2$ intersect only with $B_2^*$ and so $B_2 \cap B_1^* = \emptyset$.

In part 3, due to invariant (c) and invariant (d) part 1, $2r^* \leq r \leq \delta/2 < \delta^* /2$. So by Lemma \ref{lem:2r}, all points outside $B_1 \cup B_2$ are outliers.

\end{proof}

@@

\paragraph{Query}
At any point of the stream, we could be able to answer to a query (give the smallest $\alpha$-separated two congruent balls that covers all points except at most $z$ points).
Due to Invariants (c), we know that $B_1 \cap B_2^* = \emptyset$. 
So we are sure that, there exists a point $(B_2 \cup \Buffer) \cap B_2^* \neq \emptyset$.
In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.

\begin{lemma}
\label{lem:B2dz}
	At any point of the stream, 
	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
	then $B_2 \cap B_2^* = \emptyset$.
\end{lemma}

\begin{proof}
	due to invariant (b) part 1 and invariant (a) we know that $r \leq \delta/2 < \delta^*/2$. 
	By Lemma \ref{lem:center-point}, $c_p \in B_1^* \cap B_2^*$. 
	Since $c_p \not \in B_2^*$, then $c_p \in B_1^*$. 
	On the other hand, By Observation \ref{obs:intersection}, $B_2$ intersect with at most one of $B_1^*$ and $B_2^*$. So as a result, $B_2 \cap B_2^* = \emptyset$.
\end{proof}

As a result of Lemma \ref{lem:B2dz}, when $|B_2| \geq \dz$, we are sure that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
So if $|B_2| \ge \dz$, then our candidates $C$ for $c_2$ are $\{c_2\} \cup \Buffer$. Our Query algorithm, works as follows.

For each candidate $c \in C$, \Cref{alg:query} constructs $B'_1(c_1, \max \{\delta, \radius{c} \})$ and $B'_2(c, \radius{c})$. 
First, consider the candidate $c$ that equals to current $c_2$, then $B_1 = B'_1$. 
Since $\radius{c_2} \leq r \leq \delta/2$ (invariant (b) part 1) and $B'_2 \subset B_2$ then we don't need to construct any new set. 
In general case, when $c \neq c_2$, we know that $B_1 \subset B'_1$, so we just need to see which of $\Buffer \cap B_2$ points located in $B'_1$.
When $|B_2| \geq \dz$ and $c \neq c_2$, then it means that assumed $c_p \not \in B_2^*$. So By Lemma \ref{lem:B2dz}, $B_2$ can be added to $B'_1$ without contradicting invariant (a). 
So in this case, just need to see which points of $\Buffer$ should be added to $B'_1$. 
\Cref{alg:query} use functions \textproc{AddToB$'_1$} and \textproc{AddToB$'_2$} for adding a point to $B'_1$ and $B'_2$ respectively. 
Their definition are totally same as functions \textproc{AddToB$_1$} and \textproc{AddToB$_2$} except that, they add point to $B'_i$ instead of $B_i$($i = 1, 2$).

As \Cref{alg:query}, consider all valid cases of $c$, for one of $c \in C$, $c \in B_2^*$. 
Consider that $c$ as $c^*$ and corresponding $B'_1$ and $B'_2$ as $B''_1$ and $B''_2$. 
Since $1 \leq \frac{\len{c_1 c^*}}{\alpha^*} < \frac{\len {c_1 c^*}}{\alpha r^*}$(By Observation \ref{obs:c+4}) then $2r^* \leq \radius{c^*}$ and as a result $B^*_1 \subset B''_1$ and $B^*_2 \subset B''_2$ (By Lemma \ref{lem:2r}).
On the other hand, due to invariant (a) and distance of new points added to $B''_1$ compare to $B_1$ is less than $\len{c_1 p} \leq \max \{\delta, \radius{c^*} \}$, so $B''_1 \cap B_2^* = \emptyset$.
As a result $B''_1$ and $B''_2$ totally covers $B_1^*$  and $B_2^*$ respectively, with some extra outlier points and remaining points in $\Buffer$ are certainly outliers.
The only unknown part is that \Cref{alg:query} does not know how many outliers are in $B''_1$ and $B''_2$.
So \Cref{alg:compute-min} tries all possible cases and choose the one with the minimum radius.

\begin{algorithm}
\caption{\sc Query} 
\algsetup{indent=1.5em}
\label{alg:query}
\begin{algorithmic}[1]
%\Function{Query}{}
	\STATE solutions $\gets [\Call{ComputeMin}{B_1, B_2, \Buffer}]$

	\STATE candidates $\gets \Buffer$
	\IF {$\card{B_2} < \dz$}
		\STATE candidates $\gets \Buffer \cup B_2 \setminus \set{c_2}$
	\ELSE
		\STATE $B_1 \gets B_u$
	\ENDIF

	\STATE $\delta_0 = \delta$
	\FOR{$c_2 \in$ candidates}
		\STATE $\rc  \gets \frac{2}{\alpha} \len{c_1 c_2}$
		\STATE $B'_1 \gets B_1$, $\delta \gets \max \{ \delta_0, r \}$
		\STATE $B'_2 \gets \emptyset$, $\Buffer' \gets \emptyset$ 
		\FOR{$p \in$ candidates}
			\IF {\NOT (\Call{AddToB$'_1$}{$p$} \OR \Call{AddToB$'_2$}{$p$})}
				\STATE add $p$ to $\Buffer'$
			\ENDIF
		\ENDFOR
		\STATE add \Call{ComputeMin}{$B'_1$, $B'_2$, $\Buffer'$} to solutions
	\ENDFOR
	\RETURN $\min\set{\text{solutions}}$
%\EndFunction
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{\sc ComputeMin($B'_1, B'_2, \text{\rm Buffer}$)} 
\algsetup{indent=1.5em}
\label{alg:compute-min}
\begin{algorithmic}[1]
%\Function{ComputeMin}{$B_1$, $B_2$, Buffer}
	\STATE solutions $\gets [\,]$
	\FOR{$k \gets 0, \dots,(z - \card{\mbox{Buffer}})$}
		\STATE $r_1 \gets \Call{1-Center}{B'_1, k}$
		\STATE $r_2 \gets \Call{1-Center}{B'_2, z - \card{\mbox{Buffer}} - k}$
		\STATE add $\max \set{r_1, r_2}$ to solutions
	\ENDFOR
	\RETURN $\min\set{\text{solutions}}$
%\EndFunction
\end{algorithmic}
\end{algorithm}

@@

\subsection{The Case $\delta^* \leq \alpha r^*$}
\label{subsec:smaller}
Our idea in this section is derived from~\cite{ahn2014computing, kim2014improved}. To avoid duplication, we just outline the important parts of their algorithm and our modifications to it. Kim's algorithm has $10$ different states (\Cref{fig:dag}). In each step one or many of the states can be valid and their algorithm considers all of them in parallel. In each state, there exist at most two balls. A transition between the states occurs whenever a point not covered by any of the two balls has arrived in the stream. This transition graph starts with a blank node (with no balls) and has depth four (without considering the end nodes). It is straightforward to see that this transition graph is a DAG.
Our modification is on the transition part.
Points that are covered by current solution can safely be ignored, as they do not cause any transitions in the state, and only those points that lie outside the solution are candidates for being an outlier.
In each state the number of points that should be considered as outliers is unknown. So all the possible choices should be considered. It is sufficient to have four integers, $n_1,\dots, n_4$ representing the number of outliers in depth $1$ to $4$, such that $\sum_{i=1}^{4} n_i=z$. 
The modified algorithm is presented in \Cref{alg:smallc}.
In this algorithm, \textproc{NthOutlier}$(n,p)$ returns the $n$-th point 
arriving after $p$ in $P$ that does not lie in the current candidate solution.

\begin{figure}
\centering
\begin{tikzpicture}
  [scale=.75,auto=left,every node/.style={circle,fill=blue!15}]
 \tikzset{edge/.style = {->,> = latex'}}
  \node (1) at (1,2) {1};
  \node (2a) at (3,1)  {2a};
  \node (3a) at (3,4)  {3a};
  \node (2b) at (5,0)  {2b};
  \node (3b) at (5,2)  {3b};
  \node (3d) at (5,4)  {3d};
  \node (2c) at (7,0)  {2c};
  \node (3c) at (7,2)  {3c};
  \node (3e) at (7,4)  {3e};
  \node (E) at (9, 2) {E};

  \foreach \from/\to in {1/2a,1/3a,2a/2b,2b/2c,2c/E,3a/3b,3a/3b,3a/3d,3b/3c,3d/3e,3c/E,3e/E}
    \draw[edge] (\from) to (\to);

\end{tikzpicture}
\caption{State Transition of Kim \etal \cite{kim2014improved}} algorithm \label{fig:dag}
\end{figure}
